Analysis of Global Crises and Their Impact on Interational Well-Being

### 2024-11-15 Draft.Rmd
Update Draft.Rmd

# Purpose
This study aims to

@@

## \<\<Cyclones Data\>\>
```{r load_data1}
cyclones_data <- read_parquet("cyclones_data.parquet")
world <- ne_countries(scale = "medium", returnclass = "sf")

@@

happiness <- happiness |>
  left_join(
    world |>
      mutate(
        centroid = st_centroid(geometry),
        latitude = st_coordinates(centroid)[, 2],
        hemisphere = ifelse(latitude > 0, "North", "South"),
        distance_to_equator_km = as.numeric(st_distance(centroid, equator)) / 1000
      ) |>
      select(name, hemisphere, distance_to_equator_km) |>
      rename(country = name),
    by = "country"
  )

@@

`happiness` dataset is global census on a countries economic, social, and political stability provided by World Happiness Report.

@@

We explored many aspects of the data, but will demonstrate three. These are \<\<Geographic and environmental Factors VS a countries overall well being\>\>, \<\<Covid Cases Vs perception of corruption\>\>, and \<<Freedom to Make Life Choices & Climate Awareness (OR DISTANCE VS COVID)>\>

>>>>

# Purpose

This study aims to

@@

## \<\<Cyclones Data\>\>

```{r load_data1}
cyclones_data <- read_parquet("cyclones_data.parquet")
world <- ne_countries(scale = "medium", returnclass = "sf")

@@

happiness <- happiness |>
  left_join(
    world |>
      mutate(
        centroid = st_centroid(geometry),
        latitude = st_coordinates(centroid)[, 2],
        hemisphere = ifelse(latitude > 0, "North", "South"),
        distance_to_equator_km = as.numeric(st_distance(centroid, equator)) / 1000
      ) |>
      select(name, hemisphere, distance_to_equator_km) |>
      rename(country = name),
    by = "country"
  )
happiness

@@

the `happiness` dataset was loaded, containing data on countries' economic, social, and political stability from the World Happiness Report. To ensure consistency across datasets, some country names were adjusted to match the naming conventions in the `world_map` dataset. This adjustment was necessary for accurate geographic mapping. After renaming, the `happiness` dataset was joined with `world_map` to incorporate latitude and longitude coordinates for each country, enabling the visualization of global data trends on a map. Additional geographic information was also added, including the distance of each country from the equator and hemisphere designation, by using centroids of each country's polygon in the `world` dataset. This enhancement facilitates spatial analysis based on proximity to the equator and hemisphere differences.

@@

We explored many aspects of the data, but will demonstrate three. These are \<\<Geographic and environmental Factors VS a countries overall well being\>\>, \<\<Covid Cases Vs perception of corruption\>\>, and \<\<Freedom to Make Life Choices & Climate Awareness (OR DISTANCE VS COVID)\>\>
